
\noindent
\textbf{	
	Gronat, P., Obozinski, G., Sivic, J., Pajdla, T. (2013)
	Learning and calibrating per-location classifiers for visual place recognition,  
	\textit{IEEE Conference on Computer Vision and Pattern Recognition (CVPR), p.907-914}
	[cited by 39]
}


\noindent
Arandjelovic, R., $\&$ Zisserman, A. (2014, November). DisLocation: Scalable descriptor distinctiveness for location recognition. In Asian Conference on Computer Vision (pp. 188-204). Springer International Publishing.


\noindent
Donoser, M., $\&$ Schmalstieg, D. (2014). Discriminative feature-to-point matching in image-based localization. In Proceedings of the IEEE Conference on Computer Vision and Pattern Recognition (pp. 516-523).

\noindent
Lu, G., Yan, Y., Ren, L., Saponaro, P., Sebe, N., $\&$ Kambhamettu, C. (2016). Where am i in the dark: Exploring active transfer learning on the use of indoor localization based on thermal imaging. Neurocomputing, 173, 83-92.

\noindent
Arandjelović, R., Gronat, P., Torii, A., Pajdla, T., $\&$ Sivic, J. (2015). NetVLAD: CNN architecture for weakly supervised place recognition. arXiv preprint arXiv:1511.07247.

\noindent
Weyand, T., Kostrikov, I., $\&$ Philbin, J. (2016). Planet-photo geolocation with convolutional neural networks. arXiv preprint arXiv:1602.05314.

\noindent
Tang, K., Paluri, M., Fei-Fei, L., Fergus, R., $\&$ Bourdev, L. (2015). Improving image classification with location context. In Proceedings of the IEEE International Conference on Computer Vision (pp. 1008-1016).

\noindent
Weyand, T., $\&$ Leibe, B. (2015). Visual landmark recognition from internet photo collections: A large-scale evaluation. Computer Vision and Image Understanding, 135, 1-15.

\noindent
Le Barz, C., Thome, N., Cord, M., Herbin, S., $\&$ Sanfourche, M. (2014, September). Global robot ego-localization combining image retrieval and hmm-based filtering. In 6th Workshop on Planning, Perception and Navigation for Intelligent Vehicles (pp. 6-p).

\noindent
Gopalan, R. (2015). Hierarchical sparse coding with geometric prior for visual geo-location. In Proceedings of the IEEE Conference on Computer Vision and Pattern Recognition (pp. 2432-2439).

\noindent
Li, X., Larson, M., $\&$ Hanjalic, A. (2015). Global-scale location prediction for social images using geo-visual ranking. IEEE Transactions on Multimedia, 17(5), 674-686.


\noindent
Modolo, D., Vezhnevets, A., Russakovsky, O., $\&$ Ferrari, V. (2015, June). Joint calibration of ensemble of exemplar svms. In 2015 IEEE Conference on Computer Vision and Pattern Recognition (CVPR) (pp. 3955-3963). IEEE.

\noindent
Fernando, B., Tommasi, T., $\&$ Tuytelaars, T. (2015). Location recognition over large time lags. Computer Vision and Image Understanding, 139, 21-28.

\noindent
Torii, A., Dong, Y., Okutomi, M., Sivic, J., $\&$ Pajdla, T. (2014). Efficient Localization of Panoramic Images Using Tiled Image Descriptors. Information and Media Technologies, 9(3), 351-355.


\noindent
Jin Kim, H., Dunn, E., $\&$ Frahm, J. M. (2015). Predicting Good Features for Image Geo-Localization Using Per-Bundle VLAD. In Proceedings of the IEEE International Conference on Computer Vision (pp. 1170-1178).

\noindent
Aubry, M., Russell, B. C., $\&$ Sivic, J. (2015). Visual geo-localization of non-photographic depictions via 2D-3D alignment. Visual Analysis and Geolocalization of Large-Scale Imagery.

\noindent
Mousavian, A., Košecká, J., $\&$ Lien, J. M. (2015, May). Semantically guided location recognition for outdoors scenes. In 2015 IEEE International Conference on Robotics and Automation (ICRA) (pp. 4882-4889). IEEE.


\noindent
Le Barz, C., Thome, N., Cord, M., Herbin, S., $\&$ Sanfourche, M. (2015, September). Exemplar based metric learning for robust visual localization. In Image Processing (ICIP), 2015 IEEE International Conference on (pp. 4342-4346). IEEE.


\noindent
Le Barz, C., Thome, N., Cord, M., Herbin, S., $\&$ Sanfourche, M. (2015). Absolute geo-localization thanks to Hidden Markov Model and exemplar-based metric learning. In Proceedings of the IEEE Conference on Computer Vision and Pattern Recognition Workshops (pp. 9-17).

\noindent
Girdhar, R., Fouhey, D. F., Kitani, K. M., Gupta, A., $\&$ Hebert, M. (2016, March). Cutting through the clutter: Task-relevant features for image matching. In 2016 IEEE Winter Conference on Applications of Computer Vision (WACV) (pp. 1-9). IEEE.


\noindent
Said, S. H., Boujelbane, I., $\&$ Zaharia, T. (2014, September). Recognition of urban buildings with spatial consistency and a small-sized vocabulary tree. In 2014 IEEE Fourth International Conference on Consumer Electronics Berlin (ICCE-Berlin) (pp. 350-354). IEEE.

\noindent
Charles, J., Pfister, T., Magee, D., Hogg, D., $\&$ Zisserman, A. (2015). Personalizing Human Video Pose Estimation. arXiv preprint arXiv:1511.06676.


\noindent
Sivic, J. (2014). Visual search and recognition of objects, scenes and people (Doctoral dissertation, Ecole Normale Supérieure de Paris-ENS Paris).


\noindent
Gopalan, R. (2015). Hierarchical Sparse Coding With Geometric Prior For Visual Place Recognition. IEEE Computer Society Conference on Computer Vision and Pattern Recognition (CVPR).


\noindent
Becattini, F., Seidenari, L., $\&$ Del Bimbo, A. (2016, June). Indexing Ensembles of Exemplar-SVMs with rejecting taxonomies. In Content-Based Multimedia Indexing (CBMI), 2016 14th International Workshop on (pp. 1-6). IEEE.


\noindent
Sinha, S. N., Hedau, V., Zitnick, C. L., $\&$ Szeliski, R. (2016). A Memory Efficient Discriminative Approach for Location-Aided Recognition. In Large-Scale Visual Geo-Localization (pp. 279-298). Springer International Publishing.

\noindent
Mousavian, A., $\&$ Kosecka, J. (2016). Semantic Image Based Geolocation Given a Map. arXiv preprint arXiv:1609.00278.


\noindent
Liu, P., Yang, P., Wang, C., Huang, K., $\&$ Tan, T. (2016). A Semi-Supervised Method for Surveillance-Based Visual Location Recognition.


\noindent
Wang, J., Cheng, Y., $\&$ Feris, R. S. (2016). Walk and Learn: Facial Attribute Representation Learning from Egocentric Video and Contextual Data. arXiv preprint arXiv:1604.06433.


\noindent
Choi, J., Larson, M., Li, X., Friedland, G., $\&$ Hanjalic, A. (2016). Where to be wary: The impact of widespread photo-taking and image enhancement practices on users' geo-privacy. arXiv preprint arXiv:1603.01335.

\noindent
Kim, H. J. (2014). Place Recognition Using Reliable Features.

\noindent
Mousavian, A., $\&$ Košecka, J. Semantically Aware Bag-of-Words for Localization.

\noindent
Tapu, R., Mocanu, B., $\&$ Zaharia, T. (2016). A computer vision-based perception system for visually impaired. Multimedia Tools and Applications, 1-37.

\noindent
Sattler, T., Havlena, M., Schindler, K., $\&$ Pollefeys, M., Large-Scale Location Recognition and the Geometric Burstiness Problem.


\noindent
Li, X., Larson, M. A., $\&$ Hanjalic, A. (2016). Geo-distinctive Visual Element Matching for Location Estimation of Images. arXiv preprint arXiv:1601.07884.



\noindent
Modolo, D., Vezhnevets, A., $\&$ Ferrari, V. Context Forest for Object Class Detection.


\noindent
Kumar, D. (2016). Deep Learning Based Place Recognition for Challenging Environments.

\noindent
Zisserman, A., Arandjelović, R., $\&$ Church, C. Advancing Large Scale Object Retrieval.










\vfill
\newpage

\noindent
\textbf{
	Arandjelovic, R., Gronat, P., Torii, A., Pajdla, T., Sivic, J. (2016) 
	NetVLAD: CNN architecture for weakly supervised place recognition, R. Arandjelovic, P.
	\textit{IEEE Conference on Computer Vision and Pattern Recognition (CVPR)}.
	[cited by 20]
}

\noindent
Tolias, G., Sicre, R.,$\&$ Jégou, H. (2015). Particular object retrieval with integral max-pooling of CNN activations. arXiv preprint arXiv:1511.05879.


\noindent
Razavian, A. S., Sullivan, J., Carlsson, S.,$\&$ Maki, A. (2016). [Paper] Visual Instance Retrieval with Deep Convolutional Networks. ITE Transactions on Media Technology and Applications, 4(3), 251-258.

\noindent
Arroyo, R., Alcantarilla, P. F., Bergasa, L. M.,$\&$ Romera, E. (2016). Fusion and binarization of CNN features for robust topological localization across seasons. In IEEE/RSJ IROS.


\noindent
Zheng, L., Yang, Y.,$\&$ Tian, Q. (2016). SIFT Meets CNN: A Decade Survey of Instance Retrieval. arXiv preprint arXiv:1608.01807.

\noindent
Valigi, N. How can Deep Learning help Robotics and SLAM.

\noindent
Durand, T., Thome, N.,$\&$ Cord, M. WELDON: Weakly Supervised Learning of Deep Convolutional Neural Networks.

\noindent
Gordo, A., Almazan, J., Revaud, J.,$\&$ Larlus, D. (2016). End-to-end Learning of Deep Visual Representations for Image Retrieval. arXiv preprint arXiv:1610.07940.

\noindent
Mohedano, E., Salvador, A., McGuinness, K., Marques, F., O'Connor, N. E.,$\&$ Giro-i-Nieto, X. (2016). Bags of Local Convolutional Features for Scalable Instance Search. arXiv preprint arXiv:1604.04653.

\noindent
Schönberger, J. L., Price, T., Sattler, T., Frahm, J. M.,$\&$ Pollefeys, M. A Vote-and-Verify Strategy for Fast Spatial Verification in Image Retrieval.

\noindent
Alzu'bi, A., Amira, A.,$\&$ Ramzan, N. (2016, August). Compact Root Bilinear CNNs for Content-Based Image Retrieval. In Image, Vision and Computing (ICIVC), International Conference on (pp. 41-45). IEEE.

\noindent
Ustinova, E.,$\&$ Lempitsky, V. (2016). Learning Deep Embeddings with Histogram Loss. arXiv preprint arXiv:1611.00822.

\noindent
Zhou, Q., Wang, C., Liu, P., Li, Q., Wang, Y.,$\&$ Chen, S. (2016). Distribution Entropy Boosted VLAD for Image Retrieval. Entropy, 18(8), 311.

\noindent
Amato, G., Falchi, F., Gennaro, C.,$\&$ Vadicamo, L. (2016, October). Deep Permutations: Deep Convolutional Neural Networks and Permutation-Based Indexing. In International Conference on Similarity Search and Applications (pp. 93-106). Springer International Publishing.


\noindent
Tang, P., Wang, X., Shi, B., Bai, X., Liu, W.,$\&$ Tu, Z. (2016). Deep FisherNet for Object Classification. arXiv preprint arXiv:1608.00182.

\noindent
Lan, Z. (2016). Towards Usable Multimedia Event Detection from Web Videos (Doctoral dissertation, Disney Research).

\noindent
De Nadai, M., Vieriu, R. L., Zen, G., Dragicevic, S., Naik, N., Caraviello, M., Hidalgo, C. A.,Sebe, N.,$\&$ Lepri, B. (2016, October). Are Safer Looking Neighborhoods More Lively?: A Multimodal Investigation into Urban Life. In Proceedings of the 2016 ACM on Multimedia Conference (pp. 1127-1135). ACM.

\noindent
Markuš, N., Pandžić, I. S.,$\&$ Ahlberg, J. (2016). Learning Local Descriptors by Optimizing the Keypoint-Correspondence Criterion. arXiv preprint arXiv:1603.09095.

\noindent
Verbeek, J., Machine learning solutions to visual recognition problems.

\noindent
Bilen, C., Zepeda, J.,$\&$ Pérez, P. The CNN News Footage Datasets: Enabling Supervision in Image Retrieval.

\noindent
Radenović, F., Tolias, G.,$\&$ Chum, O. (2016). CNN Image Retrieval Learns from BoW: Unsupervised Fine-Tuning with Hard Examples. arXiv preprint arXiv:1604.02426.


\vfill
\newpage
\noindent
\textbf{
	Gronat, P., Havlena, M., Sivic, J., Pajdla, T. (2011) 
	Building streetview datasets for place recognition and city reconstruction. 
	\textit{Tech. Rep. CTU-CMP-2011-16, Czech Tech University.}
	[cited by 8]
}


\noindent
Doersch, C., Singh, S., Gupta, A., Sivic, J., $\&$ Efros, A. (2012). What makes paris look like paris?. ACM Transactions on Graphics, 31(4).


\noindent
Fang, Q., Sang, J., $\&$ Xu, C. (2013, October). Giant: Geo-informative attributes for location recognition and exploration. In Proceedings of the 21st ACM international conference on Multimedia (pp. 13-22). ACM.


\noindent
Fang, Q., Sang, J., $\&$ Xu, C. (2014). Discovering geo-informative attributes for location recognition and exploration. ACM Transactions on Multimedia Computing, Communications, and Applications (TOMM), 11(1s), 19.



\noindent
Doersch, C., Singh, S., Gupta, A., Sivic, J., $\&$ Efros, A. A. (2015). What makes Paris look like Paris?. Communications of the ACM, 58(12), 103-110.


\noindent
Verstockt, S., Gerke, M., $\&$ Kerle, N. (2015). Geolocalization of Crowdsourced Images for 3-D Modeling of City Points of Interest. IEEE Geoscience and Remote Sensing Letters, 12(8), 1670-1674.


\noindent
Bansal, A., $\&$ Singh, K. K. Storytelling Patches: Predicting Tourist Spots in a City.


\noindent
Doersch, C. Data Analysis Project: What Makes Paris Look like Paris?.


\noindent
\cntext{董亜飛, 鳥居秋彦, $\&$ 奥富正敏. (2013). BoF の分割表現を用いた画像検索による自己位置・方位推定. 情報処理学会研究報告 (コンピュータビジョンとイメージメディア}
(CVIM) ), 1-6.